\documentclass[12pt,a4paper]{article}

% Basic packages only (compatible with TeX Live Basic)
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{enumitem}

% Page geometry
\geometry{margin=2.5cm}

% Colors
\definecolor{cihprimary}{HTML}{38B2AC}
\definecolor{cihsecondary}{HTML}{F37021}
\definecolor{cihdark}{HTML}{1E293B}
\definecolor{cihmuted}{HTML}{64748B}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=cihprimary,
    urlcolor=cihsecondary,
    pdftitle={CIH Wallet - Features Documentation},
    pdfauthor={CIH Bank}
}

% Simple quote environment
\newenvironment{myquote}{\begin{quote}\itshape}{\end{quote}}

% Document
\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace*{3cm}
    
    {\Huge\bfseries\textcolor{cihprimary}{CIH Wallet}\par}
    \vspace{0.5cm}
    {\Large\textcolor{cihdark}{The Future of Banking is Here}\par}
    
    \vspace{2cm}
    
    \begin{myquote}
        \centering
        \Large Your Money. Your Rules. Your Life.
    \end{myquote}
    
    \vspace{2cm}
    
    {\large Morocco's most innovative mobile banking experience designed for the Gen-Z hustler, the ambitious entrepreneur, and everyone who believes banking should be as smart as they are.\par}
    
    \vfill
    
    {\large\textcolor{cihmuted}{Features \& Technical Documentation}\par}
    \vspace{1cm}
    {\normalsize\textcolor{cihmuted}{\textcopyright\ 2024 CIH Bank. All rights reserved.}\par}
\end{titlepage}

\tableofcontents
\newpage

% ============================================
% PART 1: USER FEATURES
% ============================================
\part{User Features}

\section{Instant P2P Transfers}

\subsection{The Problem}
You're at a caf\'e with friends. The bill comes. Someone pays. Now you need to send them money. Traditional banks? They'll make you wait. Fill out forms. Pay hefty fees. \textit{It's 2024 -- why is sending money still so hard?}

\subsection{The Solution}
\textbf{Send money in seconds.} Just tap, enter the amount, and boom -- your friend has the cash before the waiter comes back with the receipt.

\begin{itemize}[leftmargin=*]
    \item \textbf{Instant transfers} to any CIH Wallet user
    \item \textbf{Just a phone number} -- no complicated RIBs or IBANs
    \item \textbf{Minimal fees} -- keep more of your money
    \item \textbf{Real-time confirmation} -- know it's done, instantly
\end{itemize}

% ============================================
\section{Shop \& Split -- Buy Now, Pay Later (BNPL)}

\subsection{The Problem}
You found the perfect jacket at Zara. The laptop you need is at Electroplanet. But your budget says ``wait until payday.'' Traditional credit? High interest. Complicated approval. Weeks of waiting. \textit{Your dreams shouldn't have to wait.}

\subsection{The Solution}
\textbf{Split it in 4. Zero interest. Zero hassle.}

With \textbf{Shop \& Split}, you can shop at Morocco's favorite stores and pay in 4 easy monthly installments. No credit checks. No hidden fees. Just pure freedom.

\subsubsection{Partner Stores}
\begin{itemize}[leftmargin=*]
    \item \textbf{Marjane} -- Your grocery runs, split smoothly
    \item \textbf{Zara} -- Fashion now, pay later
    \item \textbf{Ikea} -- Build your dream home, one payment at a time
    \item \textbf{Decathlon} -- Gear up for your goals
    \item \textbf{Electroplanet} -- Tech upgrades made affordable
    \item \textbf{Virgin Megastore} -- Entertainment without the wait
\end{itemize}

\subsubsection{How It Works}
\begin{enumerate}
    \item Shop at any partner store
    \item Choose ``Split in 4'' at checkout
    \item Pay 25\% today
    \item Pay the rest over 3 months
    \item \textbf{That's it. No interest. No tricks.}
\end{enumerate}

% ============================================
\section{Daret -- Traditional Savings, Reimagined}

\subsection{The Problem}
You know Daret -- the trusted Moroccan tradition where friends pool money together. But managing it manually? Tracking who paid? Chasing late payments? \textit{It's a headache nobody asked for.}

\subsection{The Solution}
\textbf{Daret, but make it digital.}

Create or join savings circles with friends and family. We handle the tracking, the reminders, and the math. You just focus on saving.

\begin{itemize}[leftmargin=*]
    \item \textbf{Invite your circle} -- Friends, family, colleagues
    \item \textbf{Set your schedule} -- Weekly, bi-weekly, monthly
    \item \textbf{Automatic reminders} -- No more awkward ``did you pay?'' texts
    \item \textbf{Transparent tracking} -- Everyone sees who paid and who's next
    \item \textbf{Build trust, build wealth} -- Together
\end{itemize}

% ============================================
\section{Borrow \& Lend -- P2P Lending Made Simple}

\subsection{The Problem}
Your friend needs 500 DH until payday. You want to help, but tracking debts on paper (or worse, in your head) leads to forgotten promises and awkward conversations. \textit{Money and friendships shouldn't be enemies.}

\subsection{The Solution}
\textbf{Request money. Lend money. Track it all.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Send borrow requests} -- No shame, just a simple tap
    \item \textbf{Accept or decline} -- Your money, your choice
    \item \textbf{Automatic tracking} -- We remember so you don't have to
    \item \textbf{Gentle reminders} -- Stay on top of who owes what
    \item \textbf{Keep friendships intact} -- Money drama, eliminated
\end{itemize}

% ============================================
\section{Multi-Wallet Management}

\subsection{The Problem}
You've got different financial goals -- savings for that trip to Marrakech, a budget for online shopping, emergency funds. But one account for everything? That's chaos. \textit{Your money deserves organization.}

\subsection{The Solution}
\textbf{Create wallets for every goal.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Vacation Fund} -- Watch your dream trip get closer
    \item \textbf{Shopping Wallet} -- Guilt-free spending
    \item \textbf{Emergency Savings} -- Peace of mind, always
    \item \textbf{Custom Goals} -- Name it. Fund it. Achieve it.
\end{itemize}

Switch between wallets in a tap. See your balances at a glance. Stay in control, always.

% ============================================
\section{Smart Analytics}

\subsection{The Problem}
``Where did all my money go?'' -- The monthly question nobody wants to ask. Spreadsheets are boring. Bank statements are confusing. \textit{Understanding your spending shouldn't require a finance degree.}

\subsection{The Solution}
\textbf{Beautiful charts. Clear insights. Smarter spending.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Category Breakdown} -- Food, Shopping, Transport, Entertainment
    \item \textbf{Income vs. Spending} -- Are you winning or losing?
    \item \textbf{Spending Trends} -- Track your progress over time
    \item \textbf{Tap for Details} -- See exactly what you spent and where
\end{itemize}

\textit{Finally, an answer to ``Where did my money go?''}

% ============================================
\section{Gigs -- Earn Extra Cash}

\subsection{The Problem}
You've got skills. You've got time. But finding opportunities? That's the hard part. Freelance platforms take huge cuts. Local jobs are hard to find. \textit{Your hustle deserves better.}

\subsection{The Solution}
\textbf{Discover gigs near you. Get paid instantly.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Browse opportunities} -- Delivery, tutoring, design, and more
    \item \textbf{Transparent pay} -- Know exactly what you'll earn
    \item \textbf{Instant payouts} -- Get paid directly to your wallet
    \item \textbf{Build your reputation} -- Great reviews = more gigs
\end{itemize}

\textit{Turn your free time into cash flow.}

% ============================================
\section{Map -- Find ATMs \& Agents}

\subsection{The Problem}
You need cash, but which ATM is closest? Is it even working? Where's the nearest CIH agent? \textit{Wandering around hoping to find one isn't a strategy.}

\subsection{The Solution}
\textbf{Every CIH point, on your map.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Real-time locations} -- ATMs, agents, branches
    \item \textbf{Get directions} -- One tap to navigate
    \item \textbf{ATM status} -- Know before you go
    \item \textbf{Filter by service} -- Cash out, deposits, support
\end{itemize}

% ============================================
\section{Smart Notifications}

\begin{itemize}[leftmargin=*]
    \item \textbf{Transaction alerts} -- Every credit, every debit
    \item \textbf{Borrow requests} -- Someone needs your help
    \item \textbf{Payment reminders} -- Never miss a deadline
    \item \textbf{Milestone celebrations} -- Hit your savings goal? We'll cheer!
\end{itemize}

% ============================================
\section{Security}

Built on CIH Bank's proven infrastructure with enterprise-grade security:

\begin{itemize}[leftmargin=*]
    \item \textbf{OTP Verification} -- Every sensitive action, protected
    \item \textbf{Encrypted transactions} -- Your data, locked tight
    \item \textbf{Device authentication} -- Only you can access your wallet
    \item \textbf{Real-time fraud detection} -- We watch, so you don't have to
\end{itemize}

\newpage

% ============================================
% PART 2: BEHAVIORAL INTELLIGENCE
% ============================================
\part{Behavioral Intelligence}

\begin{myquote}
This isn't just an app. It's a data goldmine.
\end{myquote}

\section{Lifetime Financial Profiling}

\subsection{The Opportunity}
Traditional banks only know their customers through forms and credit scores. They guess. They assume. They get it wrong. \textit{What if you could truly understand your customers from day one?}

\subsection{The CIH Advantage}
\textbf{Capture the customer journey from student to CEO.}

When a university student opens their first CIH Wallet, we begin building the most valuable asset in banking: \textbf{a complete financial behavior profile}.

\subsubsection{What We Track}
\begin{itemize}[leftmargin=*]
    \item \textbf{Spending Categories} -- Food, transport, entertainment, education
    \item \textbf{Cash Flow Patterns} -- When they receive money, when they spend it
    \item \textbf{Timing Behaviors} -- Do they spend on payday? Do they save at month-end?
    \item \textbf{Financial Discipline} -- Do they stick to budgets? Do they set goals?
    \item \textbf{Transaction Frequency} -- Daily spender vs. bulk buyer
\end{itemize}

\subsection{Example Customer Journey}

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Life Stage} & \textbf{What We Learn} & \textbf{What We Offer} \\
\midrule
Student & Textbooks, transport, weekends & Student discounts \\
First Job & Salary deposits, rent, shopping & Credit card, savings \\
Growing Career & Higher income, travel, dining & Premium card, investments \\
Family Life & Baby products, insurance & Home loan, family insurance \\
\bottomrule
\end{tabular}
\end{table}

\textbf{No other bank in Morocco has this data. This is CIH's moat.}

% ============================================
\section{Predictive Product Matching}

\textbf{AI-powered recommendations based on REAL behavior, not demographics.}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Detected Behavior} & \textbf{Automatic Recommendation} \\
\midrule
High taxi/transport spending & Car loan at 4.5\% \\
Consistent rent payments & Mortgage pre-qualification \\
Regular international transfers & Multi-currency account \\
Frequent BNPL usage & Credit card upgrade \\
Daret participation & Higher savings rates \\
\bottomrule
\end{tabular}
\end{table}

% ============================================
\section{Social Graph Mapping}

\subsection{The Hidden Treasure}
Every transfer tells a story. Every borrow request reveals a relationship. Every Daret circle maps a community. \textit{This is social data that even Facebook doesn't have.}

\subsection{Data Points Captured}
\begin{itemize}[leftmargin=*]
    \item \textbf{Who sends money to whom} -- And how often
    \item \textbf{Transfer amounts} -- Small (social) vs. large (family support)
    \item \textbf{Reciprocity patterns} -- Who pays back? Who doesn't?
    \item \textbf{Household detection} -- Multiple users sharing expenses = family
    \item \textbf{Business relationships} -- Regular payments = employment
    \item \textbf{Student networks} -- Dorm mates, study groups
\end{itemize}

\subsection{Business Intelligence Value}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Insight} & \textbf{Business Value} \\
\midrule
Influencer Detection & Potential brand ambassadors \\
Household Mapping & Family bundles, joint accounts \\
Employer Identification & Target salary accounts \\
Community Clusters & Targeted campaigns \\
Credit Risk Assessment & Trustworthiness indicators \\
Churn Prediction & Network-based retention \\
\bottomrule
\end{tabular}
\end{table}

\newpage

% ============================================
% PART 3: CREDIT SCORING SYSTEM
% ============================================
\part{CIH Credit Score}

\begin{myquote}
Morocco's First True Behavioral Credit System
\end{myquote}

\section{The Problem with Traditional Credit Scoring}

Morocco has \textbf{no centralized credit bureau} like FICO in the US or Experian in Europe. Banks rely on:

\begin{itemize}[leftmargin=*]
    \item Employment letters (easily forged)
    \item Salary slips (doesn't show spending behavior)
    \item Collateral (excludes young people)
    \item Gut feeling (inconsistent, biased)
\end{itemize}

\textit{Result: Millions of creditworthy Moroccans can't access credit because they have no formal ``credit history.''}

\section{The CIH Wallet Solution}

By tracking actual financial behavior within the app, CIH can build \textbf{Morocco's first true alternative credit scoring system}.

% ============================================
\section{Data Extraction by Feature}

\subsection{P2P Transfers}

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Data Extracted} & \textbf{Credit Impact} & \textbf{AI Use Case} \\
\midrule
Transfer frequency & Financial health indicator & Cash flow prediction \\
Consistent recipients & Family responsibility & Identify dependents \\
Amounts vs. balance & Discipline metric & Credit limit calc \\
Transfer timing & Bill payment patterns & Expense prediction \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Credit Score Factor: Transaction Diversity (+15 points max)}

\subsection{BNPL (Shop \& Split)}

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Data Extracted} & \textbf{Credit Impact} & \textbf{AI Use Case} \\
\midrule
On-time payments & High reliability & Loan automation \\
Plans completed & Proven track record & Credit limit increase \\
Average purchase & Predictable behavior & Recommendations \\
Missed payments & Risk flag & Early warning \\
Store categories & Lifestyle profiling & Product matching \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Credit Score Factor: BNPL Reliability (+30 points max)}

\subsection{Daret (Savings Circles)}

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Data Extracted} & \textbf{Credit Impact} & \textbf{AI Use Case} \\
\midrule
Participation rate & Financial responsibility & Savings targeting \\
Payment punctuality & Trustworthiness & Risk assessment \\
Circle completion & Commitment level & Social trust \\
Organizer role & Leadership indicator & Premium ID \\
Circle size & Peer trust level & Credibility score \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Credit Score Factor: Social Trust (+20 points max)}

\subsection{Other Features}
\begin{itemize}
    \item \textbf{Borrow \& Lend} -- Payment History (+25 points max)
    \item \textbf{Multi-Wallet} -- Financial Discipline (+10 points max)
    \item \textbf{Spending Analytics} -- Account Health (+15 points max)
    \item \textbf{Social Graph} -- Network Trust (+10 points max)
\end{itemize}

% ============================================
\section{Credit Score Calculation}

\subsection{Score Components}

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Factor} & \textbf{Weight} & \textbf{Max Points} & \textbf{Data Source} \\
\midrule
Payment History & 25\% & 25 & BNPL, P2P repayments \\
BNPL Reliability & 25\% & 30 & Shop \& Split \\
Social Trust & 15\% & 20 & Daret, network \\
Transaction Diversity & 15\% & 15 & P2P, spending \\
Financial Discipline & 10\% & 10 & Wallet management \\
Account Health & 10\% & 15 & Balance trends \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Score Ranges}

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Score} & \textbf{Grade} & \textbf{Meaning} & \textbf{Eligibility} \\
\midrule
750--850 & Excellent & Top-tier behavior & All products, best rates \\
700--749 & Good & Reliable user & Credit cards, loans \\
650--699 & Fair & Building history & Higher BNPL limits \\
600--649 & Building & New user & Standard BNPL \\
$<$600 & Limited & Needs improvement & Basic features only \\
\bottomrule
\end{tabular}
\end{table}

% ============================================
\section{AI/ML Applications}

\subsection{Credit Risk Automation}

\begin{verbatim}
INPUT:
- Transaction history (6+ months)
- BNPL repayment record
- Daret participation
- Social graph quality
- Spending patterns

OUTPUT:
- Credit Score (600-850)
- Risk Category (Low/Medium/High)
- Recommended Credit Limit
- Interest Rate Tier
- Approval Decision
\end{verbatim}

\subsection{Personalized Product Recommendations}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{User Behavior} & \textbf{AI Recommendation} \\
\midrule
High transport spending & Car loan, fuel card \\
Regular rent payments & Mortgage pre-qualification \\
Frequent BNPL usage & Credit card upgrade \\
Growing savings wallet & Investment products \\
Active Daret participation & Higher savings rates \\
International transfers & Multi-currency account \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Churn Prediction \& Fraud Detection}

\textbf{Churn Signals:} Declining transactions, decreasing balance, network leaving, failed transactions.

\textbf{Fraud Signals:} Unusual amounts, new device, new locations, rapid transfers.

\newpage

% ============================================
% PART 4: BUSINESS VALUE
% ============================================
\part{Strategic Value}

\section{The Business Value}

\subsection{For CIH}

\begin{enumerate}
    \item \textbf{Automate 80\% of credit decisions} -- Reduce manual review costs
    \item \textbf{Reduce default rates by 40\%} -- Better risk prediction
    \item \textbf{Increase loan volume 3x} -- Serve the ``unbanked'' creditworthy
    \item \textbf{Cross-sell with 5x higher conversion} -- Right product, right time
    \item \textbf{Reduce churn by 30\%} -- Predict and prevent
\end{enumerate}

\subsection{For Customers}

\begin{enumerate}
    \item \textbf{Access credit without paperwork} -- Just use the app
    \item \textbf{Build credit history by living} -- No special actions needed
    \item \textbf{Get fair rates based on behavior} -- Not assumptions
    \item \textbf{Transparent scoring} -- Know exactly why and how
    \item \textbf{Improve score over time} -- Clear path to better terms
\end{enumerate}

\section{The Vision}

\begin{myquote}
Every Moroccan who uses CIH Wallet is building their financial identity.
\end{myquote}

From the university student buying their first laptop on BNPL, to the entrepreneur managing multiple wallets, to the parent saving for their child's education through Daret -- every action is a data point.

\textbf{CIH doesn't just know its customers. CIH understands them.}

\section{Executive Summary}

\textbf{CIH Wallet isn't an expense. It's an investment in the future of banking.}

\subsection{For CIH Leadership}

\begin{enumerate}
    \item \textbf{Acquire customers YOUNG} -- Lock them in for life
    \item \textbf{Understand behavior, not just balances} -- Sell the right products
    \item \textbf{Build a social graph} -- Know relationships, predict needs
    \item \textbf{Create a data moat} -- Competitors can't replicate time
    \item \textbf{Enable AI-powered banking} -- The data foundation for tomorrow
\end{enumerate}

\subsection{The Bottom Line}

Every transaction processed by CIH Wallet adds to an irreplaceable dataset that will power CIH's competitive advantage for the next decade.

\textit{This is how you build the bank of the future.}

\section{Why CIH Wallet?}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Traditional Banking} & \textbf{CIH Wallet} \\
\midrule
Long queues & Instant everything \\
Confusing statements & Beautiful analytics \\
High fees & Minimal costs \\
Rigid savings & Flexible multi-wallets \\
Paper-based Daret & Digital TONTINE \\
Credit card applications & BNPL in seconds \\
Guessing customer needs & Knowing customer behavior \\
\bottomrule
\end{tabular}
\end{table}

\vfill

\begin{center}
\Large\textbf{CIH Wallet -- Bank Smart. Live Free.}

\vspace{1cm}

\textcolor{cihmuted}{\textcopyright\ 2024 CIH Bank. All rights reserved.}
\end{center}

\end{document}
